---
title: "Meeting Talking Points"
#subtitle: "⚔<br/>with xaringan"
author: "JooYoung Seo"
#institute: "RStudio, PBC"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      in_header: "meta.html"
---

```{r xaringan-slide-tone, echo=FALSE}
xaringanExtra::use_slide_tone()
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, middle, inverse

# Meeting Points


## Summer Defense/Graduation
## Job Searching Update
## SCAFFOLD Revision

---
class: center, middle, inverse

# Summer Defense/Graduation

## 6/14 (Mon) - 6/17 (Thu): Defense.

## 5/17 (Mon): Dissertation Dissemination to Committee.

---
class: center, middle, inverse

# Job Searching Update

## [Postdoc]: University of Carleton.

## UIUC iSchool (02/22 - 02/23).

---
class: center, middle, inverse

# SCAFFOLD Revision

## Hire editor.

## Turn in late February.
