---
title: "JooYoung's Academic Plans"
#subtitle: "⚔<br/>with xaringan"
author: "JooYoung Seo"
#institute: "RStudio, PBC"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      in_header: "meta.html"
---

```{r xaringan-slide-tone, echo=FALSE}
xaringanExtra::use_slide_tone()
```

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: center, middle, inverse

# JooYoung's Profile

* JY's latest CV: https://jooyoungseo.github.io/jy_CV/JooYoung_Seo_CV.pdf

* Personal homepage: http://jooyoungseo.com/

* Google Scholar: https://scholar.google.com/citations?user=c0x8E5YAAAAJ&hl=en

* GitHub: https://github.com/jooyoungseo

* LinkedIn: https://www.linkedin.com/in/jooyoungseo/

---

class: center, middle, inverse

# Final Defense Plan (Spring 2021)

* **May 8: commencement.**

* March 29: revised dissertation upload to the eTD website.

* **March 5: final defense.**

* Feb 15: dissertation draft for the eTD format review.

* Jan 2, 2021: Intent to Graduate Activation.

.footnote[
[1] [Spring 2021 academic calendar](https://www.registrar.psu.edu/academic-calendars/2020-21.cfm).

[2] [Important Deadlines](https://gradschool.psu.edu/completing-your-degree/important-deadlines/).
]

---

class: center, middle, inverse

# Conference Plans

* Sep 16-18: DC at the ACM Richard Tapia Celebration of Diversity in Computing Conference.

* Nov 1: full paper to the [International Conference on Learning Analytics & Knowledge](https://www.solaresearch.org/events/lak/lak21/general-call/?fbclid=IwAR2cQtjCoyV_uB05K2QTczE1G468UoFi-ieIpXyjTgto4aX0Pdqz6Y96DDU).

* ICLS/CSCL (optional)
